---
title: "Travel"
description: |
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## How to get to Santa Barbara

By air...

-   Fly directly into Santa Barbara airport!
    -   Rental car options: If you want to avoid airport rental car fees there is another Enterprise rental car location \~0.5 miles from the Santa Barbara Airport (5959 Hollister Ave Ste B, Goleta, CA 93117)
-   Fly into Los Angeles (about 90 miles, 1.5-3 hours from SB)
    -   If you rent a car from LA, you can enjoy a scenic drive along the coast to Santa Barbara - traffic is usually not bad once you get out of the immediate LAX area.
    -   The easiest bus option is the <a href="https://www.sbairbus.com/lax-shuttle-schedule-fares/">SB airbus</a> which goes directly from LAX to various locations around Goleta and Santa Barbara.
    -   Other options like Flixbus, Amtrak, and more may offer different price points, routes, and times.

By train...

-   Pacific Surfliner <a href="https://www.pacificsurfliner.com/">train</a>: we have never taken it but we hear great things!

By road...

-   You can easily drive from North, South, East, but probably not West

-   Santa Barbara is about 1-3 hours from LA, 4-5 hours from San Francisco, 12 hours from Salt Lake City, and 45 hours from Boston (depending on traffic)

## Where to stay

-   There are many nice hotels and AirBnBs around Santa Barbara
-   We have put together some <a href="https://withjoy.com/michael-and-caroline-20251004/accommodations">recommendations and discount rates</a>, but SB is a tourist town so you have many options at a wide range of styles and budgets
-   There are also beautiful campgrounds located just north and south of town (check El Capitan and Carpinteria State Beach for some of our favorites)

## 

We want to make your travel as smooth as possible so please reach out to us with any questions, ideas, or concerns!

```{r, layout="l-screen",echo=FALSE, out.width='100%'}
htmltools::tags$iframe(src = "https://withjoy.com/michael-and-caroline-20251004/accommodations", 
                       height = "1000px", 
                       width = "100%",
                       border = "none",
                       overflow = "hidden",
                       `data-external` = "1")
```